CUNY SPSS Data Science Math Homework 2

### 2018-07-21 data-science-math/Homework 2.Rmd
More work

```{r setup, include=FALSE}
library(pander)
library(tidyr)
library(gtools)
knitr::opts_chunk$set(echo = TRUE)
```

@@

$$\{AEF, ATF, AEV, AEF, CEF, CTF, CEV, CEF\}$$

@@

$$P(r|h) = \frac{25}{51} \cdot \frac{13}{52} \approx -.1225$$
```{r}
25/51 * 13/52
```

@@

@@

@@

@@

@@

@@

@@

>>>>

```{r setup, include=FALSE}
library(pander)
library(dplyr)
library(tidyr)
library(gtools)
knitr::opts_chunk$set(echo = TRUE)
```

@@

$$\{AEF, ATF, AEV, AEF, CEF, CTF, CEV, CEF\}$$
```{r}
toppings <- c('A','C')
meats <- c('E','T')
dressings <- c('F','V')

q2_data <- crossing(toppings, meats) %>%
  crossing(., dressings) %>%
  mutate(combinations = paste0(toppings, meats, dressings))

as.vector(q2_data$combinations)
```

@@

$$P(r|h) = \frac{25}{51} \cdot \frac{13}{52} \approx 0.1225$$
```{r}
25/51 * 13/52
```

@@

$$6 \times 5 \times 3 = 90$$

@@

$$P(9) = 9! = 362880$$
```{r}
die_rolls <- c('4.1','4.2','4.3','6.1','6.2','6.3','6.4','6.5','1')
q14_data <- permutations(length(die_rolls), length(die_rolls), die_rolls)
nrow(q14_data)
```

@@

$$ C(14,6) = \frac{14!}{6!(14-6)!} =  \frac{87178291200}{720\cdot 8!} = \frac{87178291200}{720\cdot 40320} = \frac{87178291200}{29030400} = 3003$$

```{r}
q15_data <- combinations(14,6)
nrow(q15_data)
```

@@

$$ C(52,3) = \frac{52!}{3!(52-3)!} =  \frac{52!}{3!\cdot 49!} = 22100$$

```{r}
q16_data <- combinations(52,3)
nrow(q16_data)
```

@@

$$ 12 \times 9 \times 5 = 540$$

```{r}
tvs <- c(1,2,3,4,5,6,7,8,9,10,11,12)
surround_sound_systems <- c(1,2,3,4,5,6,7,8,9)
dvd_players <- c(1,2,3,4,5)

q17_data <- tidyr::crossing(tvs, surround_sound_systems) %>%
  tidyr::crossing(., dvd_players)
nrow(q17_data)
```

@@

$$ C(26,5) = \frac{26!}{5!(26-5)!} =  \frac{26!}{5!\cdot 21!} = 65780$$

$$ C(5,3) = \frac{5!}{3!(5-3)!} =  \frac{5!}{3!\cdot 2!} = 10$$
$$65780 \times 10 = 657800$$
```{r}
letters <- combinations(26,5)
numbers <- combinations(5,3)
nrow(letters) * nrow(numbers)
```

@@

$$ P(10) = 10! = 3628800 $$
```{r}
letters <- c('P','o','p','u','l','a','t','i','o','n')
factorial(length(letters))
```
